troubleshooting

### 2025-05-12 README.Rmd
added prepare_diann() to support DIA-NN output.

prepared_pd_data
```

>>>>

prepared_pd_data
```
### DIA-NN

We are currently investigating how well the method works with DIA data. 
To allow for this we have created a parser to make DIA-NN output compatible with
mspms.

Note that this could be used with DIA-NN alone or with Fragpipe (MSFragger-DIA) 
uses DIA-NN for quantification. Here we are using the file output from Fragpipe.

Use caution when using this approach, we haven't thoroughly investigated how 
well DIA data works with mspms using ground truth data yet.

```{r}
precursor_filepath = system.file(
  "extdata/diann_report.pr_matrix.tsv",
  package = "mspms"
)
colData_filepath = system.file(
  "extdata/diann_colData.csv",
  package = "mspms"
)

prepared_diann_data <- prepare_diann(precursor_filepath,colData_filepath)

prepared_diann_data
```
